\documentclass{resume} % Use the custom resume.cls style
\usepackage[left=0.4 in,top=0in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace {.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\begin{document}

% Title
\begin{center}
    {\Huge \textbf{Alexis Biver}} \hspace{5cm} Metz, Grand Est, France \\
    \href{mailto:biveralexis@gmail.com}{biveralexis@gmail.com}   \hspace{1cm}     \href{https://github.com/alexisbiver}{www.github.com/alexisbiver}  \hspace{1cm} \href{https://linkedin.com/in/biver-alexis}{linkedin.com/in/biver-alexis}
\end{center}

\vspace{0.3cm}

Innovative \textbf{Machine Learning Engineer} with over 5 years of experience specializing in robotics, natural language processing (NLP), and embedded ML solutions. Proven expertise in developing production-ready models, optimizing edge-device ML applications, and contributing to open-source projects. Adept at teaching and mentoring, with a 
\centerline {strong focus on collaboration and continuous improvement.}

% Section: Core Skills
 \begin{rSection}{Core Skills}
\begin{itemize}
    \item \textbf{Programming \& Tools:} Python, Torch, Docker, FASTApi, ONNX, C++, TS, MySQL, ROS
    \item \textbf{Machine Learning:} Motion prediction, NLP, Edge-device Optimization, Diffusion Models
    \item \textbf{Languages:} French (Native), English (Professional Working Proficiency)
\end{itemize}
\end{rSection} 

% Section: Professional Experience
 \begin{rSection}{Professional Experience}
\textbf{Machine Learning Engineer} \hfill \textit{Inria, Team Larsen/HuCeBot} \\
Nancy, Grand Est, France \hfill Jan 2023 -- Dec 2024 (2 years)
\begin{itemize}
    \item Developed an open-source \href{https://github.com/hucebot/prescyent}{Python library} for motion prediction in robotics
       \item Performed benchmarks and implementations of the SOTA solutions for the library
      \item Supervision of an internship leading to a software allowing simple controls of a humanoid robot by voice
\end{itemize}

\vspace{0.2cm}

\textbf{Teaching Associate} \hfill \textit{IUT Nancy-Charlemagne} \\
Nancy, Grand Est, France \hfill March 2024 -- June 2024  (1 semester)
\begin{itemize}
    \item Delivered lectures and practical sessions on "Introduction to Network Services" for first-year IT students.
    \item Conducted Java-based exercises and evaluations.
\end{itemize}

\vspace{0.2cm}

\textbf{Machine Learning Engineer} \hfill \textit{Vivoka, R\&D} \\
Metz, France \hfill Sept 2019 -- Jan 2023 (3 years, 4 months)
\begin{itemize}
    \item Designed and optimized ML models for embedded/edge devices using PyTorch and ONNX.
    \item Developed Python APIs to serve ML solutions and ensured production readiness.
    \item Conducted research, benchmarking, and technical popularization of scientific advancements.
    \item Enhanced data collection and processing for training robust NLP models.
\end{itemize}

\vspace{0.2cm}

\textbf{Data Analyst Developer (Internship)} \hfill \textit{PwC Luxembourg, Data Services} \\
Luxembourg \hfill March 2019 -- Aug 2019 (6 months)
\begin{itemize}
    \item Executed reporting and data visualization using ETL tools and Power BI.
    \item Updated data-mining solutions in C\#.
    \item Researched and implemented a natural language understanding (NLU) approach for data augmentation.
\end{itemize}

\end{rSection} 

% Section: Education
\begin{rSection}{Education}

\textbf{Master's in Natural Language Processing} \\
\textit{Institut des sciences du Digital, Management et Cognition (IDMC)} \hfill 2017--2019

\textbf{Bachelor's in Mathematics and Computer Science} \\
\textit{Université de Lorraine} \hfill 2014--2017 \\
\end{rSection} 
\end{document}
